Hierarchical Reverberation Mapping

### 2013-10-27 Paper/ms.tex
Bunch of writing

The cross-correlation function for a single object is defined as
in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
the amount of cross correlation is calculated by looping over pairs of points
(one selected from the continuum data set, and another from the line data set),
and accumulating mass when the lag between the two points is between $\tau$
and $\tau + \delta$.
\begin{eqnarray}
X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\left(y_i - \bar{y}\right)
\left(l_j - \bar{l}\right)
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
\end{eqnarray}
The denominator is the number of pairs of points that fall within the lag range
being considered, $[\tau, \tau + \delta]$.
The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
from our 100 simulated AGN data sets.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/example_posteriors.eps}
\caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
for three objects, each analysed separately with the single-object model. For
the first object, there is a moderate ``detection'' of a lag at about 10 days.
The second object yielded an upper limit, and the third object's lag was
not well inferred.
\label{fig:example_posteriors}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution is indicated by the white circle.\label{fig:posterior}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/ccf.eps}
\caption{The stacked cross-correlation function of the simulated data.
\label{fig:ccf}}
\end{center}
\end{figure}

>>>>

We computed the stacked cross-correlation function for the 100 data sets.
The cross-correlation function for a single object is defined as
in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
the amount of cross correlation is calculated by looping over pairs of points
(one selected from the continuum data set, and another from the line data set),
and accumulating mass when the lag between the two points is between $\tau$
and $\tau + \delta$.
\begin{eqnarray}
X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\left(y_i - \bar{y}\right)
\left(l_j - \bar{l}\right)
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
\end{eqnarray}
The denominator is the number of pairs of points that fall within the lag range
being considered, $[\tau, \tau + \delta]$, denoted $n_{\rm pair}$ by
\citet{2012MNRAS.427.2701F}.
The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
from our 100 simulated AGN data sets. There is a clear peak around 10 days.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/ccf.eps}
\caption{The stacked cross-correlation function of the simulated data.
A clear peak is seen around $\tau \approx 10$ days, but the stacked CCF has a
large width. It is difficult to interpret the cause of this width, and to
determine whether the width is due to uncertainty or diversity in the sample
of AGN. These difficulties motivate the hierarchical Bayesian model.
\label{fig:ccf}}
\end{center}
\end{figure}

As the data does not contain measurements at all possible time lags, the stacked
CCF will always require some smoothing. Here, the smoothing is supplied by the
choice of a bin width $\delta$. The stacked CCF has a substantial width. One
weakness of the stacked CCF method is that it is not clear whether this width
is caused by real diversity in the sample of AGN, or whether it is simply caused
by the difficulty in measuring the lag $\bar{\tau}$ of an object with such
sparse data. By contrast, the hierarchical Bayesian approach clearly separates
these two concepts. The diversity of the population is quantified by $\sigma$,
whereas uncertainty about the central value $\mu$ is described by the
posterior distribution for $\mu$.

To implement the hierarchical Bayesian approach on the simulated data, we first
used the single-object model on each object. The results for three objects
(the same three objects shown in Figure~\ref{fig:data}) are plotted in
Figure~\ref{fig:example_posteriors}. Due to the sparse data, there is a large
amount of uncertainty about the value of $\bar{\tau}$ for each system. Some
objects do not allow any real measurement of $\bar{\tau}$, but some do, as a
result of fortuitous variability of the continuum.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/example_posteriors.eps}
\caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
for three objects, each analysed separately with the single-object model. For
the first object, there is a moderate ``detection'' of a lag at about 10 days
(although there is a small second mode above 100 days, which can be understood
by inspecting the data in Figure~\ref{fig:data}).
The second object yielded an upper limit, and the third object's lag was
not well inferred.
\label{fig:example_posteriors}}
\end{center}
\end{figure}

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. The joint posterior distribution for $\mu$ and
$\sigma$ is shown in Figure~\ref{fig:posterior}. The prior for $\mu$ and $\sigma$
was uniform inside the rectangle shown, and the posterior distribution covers
a much smaller area, indicating that the data contained a lot of information
about the hyperparameters.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution is indicated by the white star symbol.\label{fig:posterior}}
\end{center}
\end{figure}

The marginal distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$
value.

@@

\section{Conclusions}
Reverberation mapping is an important, yet observationally intensive, technique
in studies of active galaxies.
